Making Sequential Programs Deterministic

### 2019-04-06 related.tex
Add todo for Rashmi
More about Bocchino

@@

Several techniques have been proposed to test whether a
deterministic implementation conforms to its non-deterministic finite state machine~\cite{Petrenko1996,Petrenko:1993:NSM:648128.761244,Savor:1997:639710,Hierons:2004:TCD:1040993.1040998}.
\cite{Cook:2013:RNP:2491956.2491969} presents an approach that can automatically verify properties
in branching time temporal logic systems that are inherently non-deterministic. While there has been research on type systems that provide compile time determinism guarantees for parallel programs~\cite{Bocchino:2009:TES:1640089.1640097,Bocchino:2011:SND:1926385.1926447},
there hasn't been a similar effort for sequential programs.

Failing tests that are unrelated to code changes can be expensive both in terms of monetary costs and
developer effort. \cite{Herzig:2015:EDF:2819009.2819018} proposes techniques to classify tests as false alarms
if they are known to be caused by testing infrastructure or other environment issues.~\cite{Huo:2014:IOQ:2635868.2635917}
presents an approach that detects brittle assertions in tests by performing a taint analysis on inputs classified as 
controlled and uncontrolled.~\cite{ZhangJWMLEN2014} investigates the effects of test independence assumption
on other techniques such as test prioritization, selection, etc. Other approaches~\cite{BellKMD2015,Gyori:2015:RTD:2771783.2771793}
analyze test dependencies and either prevent them or use this information for other optimizations.
The approaches in \cite{Dan:2013:10.1007/978-3-642-39038-8_25,Vahabzadeh:2015:7332456} focus on differentiating bugs due to tests
from those caused by source code. While we haven't fully accounted for all nondeterministic sources due
to the environment, our technique is easily extensible by adding annotations to the corresponding classes.

>>>>

\todo{I don't see how the first two (especially the first) citations in the
  next paragraph are related to our work.  Make the connection explicit, or
  remove them.}

@@

Several techniques have been proposed to test whether a
deterministic implementation conforms to its non-deterministic finite state machine~\cite{Petrenko1996,Petrenko:1993:NSM:648128.761244,Savor:1997:639710,Hierons:2004:TCD:1040993.1040998}.
\cite{Cook:2013:RNP:2491956.2491969} presents an approach that can automatically verify properties
in branching time temporal logic systems that are inherently
non-deterministic.
Bocchino et
al.~\cite{Bocchino:2009:TES:1640089.1640097,Bocchino:2011:SND:1926385.1926447}
provide a type-and-effect system that provides compile-time determinism
guarantees for parallel programs, with a focus on barrier removal,
reasoning about interference and thread interleavings.
We believe our work to be the first verification approach
aimed at ensuring determinism in sequential programs.

Failing tests that are unrelated to code changes can be expensive both in terms of monetary costs and
developer effort. \cite{Herzig:2015:EDF:2819009.2819018} proposes techniques to classify tests as false alarms
if they are known to be caused by testing infrastructure or other environment issues.~\cite{Huo:2014:IOQ:2635868.2635917}
presents an approach that detects brittle assertions in tests by performing a taint analysis on inputs classified as 
controlled and uncontrolled.~\cite{ZhangJWMLEN2014} investigates the
effects of the test independence assumption
on other techniques such as test prioritization, selection, etc. Other approaches~\cite{BellKMD2015,Gyori:2015:RTD:2771783.2771793}
analyze test dependencies and either prevent them or use this information for other optimizations.
The approaches in \cite{Dan:2013:10.1007/978-3-642-39038-8_25,Vahabzadeh:2015:7332456} focus on differentiating bugs due to tests
from those caused by source code. While we haven't fully accounted for all nondeterministic sources due
to the environment, our technique is easily extensible by adding annotations to the corresponding classes.
